An Inception Cohort Study Quantifying How Many Registered Studies are Published.

### 2023-05-31 paper.Rmd
added extrapolation section, correcting errors.

# I need to fix the issue of number of included before and after emails.
# We included more first, and emailed people, and then removed some data.

@@

After updating our classification based on email responses, the publication rate in group 1 increased by 6% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1%. Sometimes a publication we found in the literature did not belong to the registration. If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, `r sum(registration_data$match == 1)` of the `r sum(registration_data$match != "-")` responses match with publications we found. For the `r sum(match_per_classification[3,2:3])` registrations we classified as unpublished, responses to the follow-up emails indicated that `r match_per_classification[3,3]` (`r round(100*match_per_classification[3,3]/sum(match_per_classification[3,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration. Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the `r sum(match_per_classification[4,2:3])` registrations where we were uncertain if the study was published, `r match_per_classification[4,3]` (`r round(100*(match_per_classification[4,3]/sum(match_per_classification[4,2:3])), 2)`%) of registrations matched a paper we found. Of the `r match_per_classification[4,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is often difficult to determine whether a registration is published based exclusively on the information researchers provide in their registration on the OSF.

@@

#Of the 14 published, 6 were from automatically opened registrations, out of 29 total closed projects, so 6/29 automatically opened projects we thought were unpublished were published. For the manually opened projects, 8/16 were published.
published_after_email_per_classification$published[11]
published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]
published_after_email_per_classification$published[12]
published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]

@@

# So how many of the uncertain registrations are actually published?
published_non_response_uncertain <- (published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]) + (published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10])

@@

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The `r contacted_researchers_per_publication_status$sum[3] - responses_per_publication_status$sum[3]` non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the `r contacted_researchers_per_publication_status$sum[4] - responses_per_publication_status$sum[4]` non-responses related to registrations where we remained uncertain similarly contain some published and some unpublished studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that `r unpublished_non_response_unpublished` out of `r total_assumed_unpublished_no_responses` of the registration in the unpublished classification and `r unpublished_non_response_uncertain` out of `r total_assumed_unpublished_uncertain_no_responses` of the registration in the uncertain classification are actually published.

@@

estimated_nonpublication <- data.frame(Group = c("Manually Opened", "Automatically Opened", "Total"),
                 Total_Number_of_Registrations = c(total_open, total_closed, total_open + total_closed),
                 Percentage_Included = c(round(included_before$mean,2), ""),
                 Included_estimate = round(c(c(included_before$mean) * c(total_open, total_closed), sum(c(included_before$mean) * c(total_open, total_closed))),0),
                 Published = c(round(result_manual$mean,2), round(result_auto$mean,2), ""), 
                 Published_estimate = round(c(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)), sum(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)))),0),
                 Non_Published_estimate = round(c(c(included_before$mean) * c(total_open, total_closed), sum(c(included_before$mean) * c(total_open, total_closed))) - c(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)), sum(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)))),0)
                 )

@@

Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 2)`%, for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample, we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around `r 100-round(100*result_population[4], 2)`% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009], wherever this waste is avoidable.

@@

A substantial amount of data that researchers collect is never publicly shared. Every system will have some inefficiencies, and researchers will differ in their views about when a file drawer is too large [@dickersin_factors_1992]. What is perhaps most surprising is that researchers rarely talk about how many studies they have collected that could have value for peers, and yet linger in their file drawer. Researchers might feel uneasy to honestly discuss this topic because unpublished studies are strongly associated with bias. More transparency about unpublished studies would allow our field to improve the way we work and increase the efficiency of psychological science.

>>>>

@@

After updating our classification based on email responses, the publication rate in group 1 increased by 6% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1%. Sometimes a publication we found in the literature did not belong to the registration. If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, `r sum(registration_data$match == 1)` of the `r sum(registration_data$match != "-")` responses match with publications we found. For the `r sum(match_per_classification[3,2:3])` registrations we classified as unpublished, responses to the follow-up emails indicated that `r match_per_classification[3,3]` (`r round(100*match_per_classification[3,3]/sum(match_per_classification[3,2:3]),2)`%) were unpublished, while for `r match_per_classification[3,2]` (`r round(100*match_per_classification[3,2]/sum(match_per_classification[3,2:3]),2)`%) we failed to identify the published paper based on the information in the registration. Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the `r sum(match_per_classification[4,2:3])` registrations where we were uncertain if the study was published, `r match_per_classification[4,3]` (`r round(100*(match_per_classification[4,3]/sum(match_per_classification[4,2:3])), 2)`%) of registrations matched a paper we found. Of the `r match_per_classification[4,2]` (`r round(100*match_per_classification[4,2]/sum(match_per_classification[4,2:3]),2)`%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is often difficult to determine whether a registration is published based exclusively on the information researchers provide in their registration on the OSF.

@@

# We did not get a response for 6 projects we were uncertain about, of which 1 was manually opened, and 5 were automatically opened. For the 24 registrations we were uncertain about that we did received a response for, 12 are published, and 12 are not. For the manually opened projects, 3 out of 5 were published, and for the automatically opened projects 9 out of 19 were published. We did not get responses for 6 projects, of which 5 were automatically opened, and 1 was manually opened, for which the following might hold:

published_after_email_per_classification$published[11]
published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]
published_after_email_per_classification$published[12]
published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]

@@

# So how many of the uncertain registrations we received no response for might actually published?
# 2.368421 out of 6, and 3.031579 are unpublished.

published_non_response_uncertain <- (published_after_email_per_classification$published[11] / (published_after_email_per_classification$published[11] + published_after_email_per_classification$not_published[11]) * published_after_email_per_classification$unsure[9]) + (published_after_email_per_classification$published[12] / (published_after_email_per_classification$published[12] + published_after_email_per_classification$not_published[12]) * published_after_email_per_classification$unsure[10])

@@

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The `r contacted_researchers_per_publication_status$sum[3] - responses_per_publication_status$sum[3]` non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the `r contacted_researchers_per_publication_status$sum[4] - responses_per_publication_status$sum[4]` non-responses related to registrations where we remained uncertain similarly contain some published and some unpublished studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that `r published_non_response_unpublished` out of `r total_assumed_unpublished_no_responses`  registrations in the unpublished classification and `r published_non_response_uncertain` out of `r total_assumed_unpublished_uncertain_no_responses` registrations in the uncertain classification are actually published.

@@

estimated_nonpublication <- data.frame(Group = c("Manually Opened", "Automatically Opened", "Total"),
                 Total_Number_of_Registrations = c(total_open, total_closed, total_open + total_closed),
                 Percentage_Included = c(round(100*included_before$mean,2), ""),
                 Included_estimate = round(c(c(included_before$mean) * c(total_open, total_closed), sum(c(included_before$mean) * c(total_open, total_closed))),0),
                 Published = c(round(100*result_manual$mean,2), round(100*result_auto$mean,2), ""), 
                 Published_estimate = round(c(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)), sum(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)))),0),
                 Non_Published_estimate = round(c(c(included_before$mean) * c(total_open, total_closed), sum(c(included_before$mean) * c(total_open, total_closed))) - c(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)), sum(c(c(included_before$mean) * c(total_open, total_closed) *  c(result_manual$mean, result_auto$mean)))),0)
                 )

@@

Our examination of `r sum(included_after$sum_after)` registrations led to an estimated publication rate of `r round(100*result_population[4], 2)`%, for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample to the population of all registrations up to November 2017 (for details, see the online supplement), we estimate that of the  `r estimated_nonpublication[3,4]` registered research studies on the OSF that met our inclusion criteria, `r estimated_nonpublication[3,7]` remain unpublished. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around `r 100-round(100*result_population[4], 2)`% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced [@bernal_social_1939; @chalmers_avoidable_2009], wherever this waste is avoidable.

@@

A substantial amount of data that researchers collect is never publicly shared. Every system will have some inefficiencies, and researchers will differ in their views about when a file drawer is too large [@dickersin_factors_1992]. What is perhaps most surprising is that researchers rarely talk about how many studies they have collected that could have value for peers, and yet linger in their file drawer. Researchers might find it uncomfortable to honestly discuss this topic because unpublished studies are strongly associated with bias, but our results suggest that logistical issues are a more likely reason for non-publication. More transparency about unpublished studies would allow our field to learn where we can improve how we work, thereby increasing the efficiency of psychological science.

### 2023-05-31 paper.tex
typo and running head
added extrapolation section, correcting errors.

\shorttitle{QUANTIFYING PUBLISHED REGISTERED STUDIES}

@@

\abstract{%
We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but never shared. Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62\%) were published. We estimate that 5550 out of 9544 (58\%) of registrations on the OSF are published within at least 4 years. Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community. In responses to emails asking researchers why studies remained unpublished, logistical issues (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review. Our study shows that a substantial amount of data that researchers collect is never publicly shared.
}

@@

After updating our classification based on email responses, the publication rate in group 1 increased by 6\% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1\%. Sometimes a publication we found in the literature did not belong to the registration. If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, 48 of the 76 responses match with publications we found. For the 50 registrations we classified as unpublished, responses to the follow-up emails indicated that 36 (72\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration. Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the 25 registrations where we were uncertain if the study was published, 11 (44\%) of registrations matched a paper we found. Of the 14 (28\%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is often difficult to determine whether a registration is published based exclusively on the information researchers provide in their registration on the OSF.

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The 26 non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the 6 non-responses related to registrations where we remained uncertain similarly contain some published and some unpublished studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that 19.45 out of 26 of the registration in the unpublished classification and 3.03 out of 6 of the registration in the uncertain classification are actually published.

@@

\begin{tabular}{lllllll}
\toprule
Group & \multicolumn{1}{c}{Registrations} & \multicolumn{1}{c}{\% Included} & \multicolumn{1}{c}{Included} & \multicolumn{1}{c}{\% Published} & \multicolumn{1}{c}{Published} & \multicolumn{1}{c}{Not Published}\\
\midrule
Manually Opened & 8008 & 0.55 & 4,395 & 0.86 & 3,775 & 619\\
Automatically Opened & 9042 & 0.57 & 5,150 & 0.34 & 1,775 & 3,375\\
Total & 17050 &  & 9,544 &  & 5,550 & 3,994\\
\bottomrule
\end{tabular}

@@

Our examination of 169 registrations led to an estimated publication rate of 58.15\%, for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample, we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around 41.85\% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}), wherever this waste is avoidable.

@@

A substantial amount of data that researchers collect is never publicly shared. Every system will have some inefficiencies, and researchers will differ in their views about when a file drawer is too large (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin et al., 1992}). What is perhaps most surprising is that researchers rarely talk about how many studies they have collected that could have value for peers, and yet linger in their file drawer. Researchers might feel uneasy to honestly discuss this topic because unpublished studies are strongly associated with bias. More transparency about unpublished studies would allow our field to improve the way we work and increase the efficiency of psychological science.

>>>>

\shorttitle{QUANTIFYING THE FILEDRAWER FOR REGISTERED STUDIES}

@@

\abstract{%
We quantified how many studies registered on the Open Science Framework (OSF) up to November 2017 are performed but never shared. Examining a sample of 315 registrations, of which 169 were research studies, we found that 104 (62\%) were published. We estimate that 5550 out of 9544 (58\%) registrations on the OSF are published within at least 4 years. Researchers use registries to make unpublished studies public, and the OSF policy to automatically make registrations public substantially increases the number of performed studies that become known to the scientific community. In responses to emails asking researchers why studies remained unpublished, logistical issues (e.g., lack of time, researchers changing jobs) was the most common reason, followed by null results and rejections during peer review. Our study shows that a substantial amount of data that researchers collect is never publicly shared.
}

@@

After updating our classification based on email responses, the publication rate in group 1 increased by 6\% (meaning that we failed to identify some publications corresponding to registrations) while the publication rate in group 2 decreased by 1\%. Sometimes a publication we found in the literature did not belong to the registration. If the study associated with the registration was published in another source than the one we identified, the classification remained the same, but we still counted this registration as a mismatch because we failed to identify the correct article without the help of the researchers. In total, 48 of the 76 responses match with publications we found. For the 50 registrations we classified as unpublished, responses to the follow-up emails indicated that 36 (72\%) were unpublished, while for 14 (28\%) we failed to identify the published paper based on the information in the registration. Most of the mismatches occurred when we were uncertain about whether a paper we found included the registered study because there was no link to the registration on the OSF and only some terminology in the registration and article overlapped. For the 25 registrations where we were uncertain if the study was published, 11 (44\%) of registrations matched a paper we found. Of the 14 (56\%) cases in this group that were a mismatch, 2 were indeed published but we failed to find the correct paper, and the remaining 12 were actually not published. In one special case the paper we found was indeed a match, but we decided to change the final classification to unpublished as the registration belonged to two studies and only one of the registered studies was published. Altogether, these results indicate that without contacting the researchers it is often difficult to determine whether a registration is published based exclusively on the information researchers provide in their registration on the OSF.

Due to non-response to our emails there is remaining uncertainty about the number of registrations in our sample that were eventually published. The 26 non-responses related to registrations where we could not find a publication might contain some publications that we missed, and the 6 non-responses related to registrations where we remained uncertain similarly contain some published and some unpublished studies. Researchers might be more likely to reply when their registration is actually published, or non-response might be unaffected by the publication status of their registration. Under the latter assumption, we can use the observed percentages of published studies in both categories to predict that responses from researchers would have told us that 6.55 out of 26 registrations in the unpublished classification and 2.97 out of 6 registrations in the uncertain classification are actually published.

@@

\begin{tabular}{lllllll}
\toprule
Group & \multicolumn{1}{c}{Registrations} & \multicolumn{1}{c}{\% Included} & \multicolumn{1}{c}{Included} & \multicolumn{1}{c}{\% Published} & \multicolumn{1}{c}{Published} & \multicolumn{1}{c}{Not Published}\\
\midrule
Manually Opened & 8008 & 54.88 & 4,395 & 85.91 & 3,775 & 619\\
Automatically Opened & 9042 & 56.95 & 5,150 & 34.47 & 1,775 & 3,375\\
Total & 17050 &  & 9,544 &  & 5,550 & 3,994\\
\bottomrule
\end{tabular}

@@

Our examination of 169 registrations led to an estimated publication rate of 58.15\%, for all registrations on the Open Science framework that were created before November 18, 2017. Extrapolating from our sample to the population of all registrations up to November 2017 (for details, see the online supplement), we estimate that of the 9544 registered research studies on the OSF that met our inclusion criteria, 3994 remain unpublished. Our study provides an important datapoint to understand how many studies are performed, but never shared. The possibility that around 41.85\% of research studies registered on the OSF (excluding multi-lab studies and Registered Reports) are not shared should make scientists reflect on the efficiency of scientific research. Although not all unreported studies necessarily reflect research waste, and science will never be perfectly efficient, our results suggest scientists might need to seriously engage with the question how internal inefficiency can be reduced (\protect\hyperlink{ref-bernal_social_1939}{Bernal, 1939}; \protect\hyperlink{ref-chalmers_avoidable_2009}{Chalmers \& Glasziou, 2009}), wherever this waste is avoidable.

@@

A substantial amount of data that researchers collect is never publicly shared. Every system will have some inefficiencies, and researchers will differ in their views about when a file drawer is too large (\protect\hyperlink{ref-dickersin_factors_1992}{Dickersin et al., 1992}). What is perhaps most surprising is that researchers rarely talk about how many studies they have collected that could have value for peers, and yet linger in their file drawer. Researchers might find it uncomfortable to honestly discuss this topic because unpublished studies are strongly associated with bias, but our results suggest that logistical issues are a more likely reason for non-publication. More transparency about unpublished studies would allow our field to learn where we can improve how we work, thereby increasing the efficiency of psychological science.
